\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-08 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results

\begin{figure*}[t]
\centering
\includegraphics[width=0.95\linewidth]{IEEE14marginals.png}
\caption{\small{Time evolution of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs, where $i=1,\hdots,5$, for the Kron-reduced IEEE 14 bus simulation setup described in Sec. \ref{subsec:NumSimIEEEBus}. The $5$ rows above correspond to the $5$ generator nodes--these are buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. The columns correspond to the time snapshots. The colorbar at the bottom shows the marginal PDF values.}}
\vspace*{-0.1in}
\label{fig:IEEE14marginals}
\end{figure*}

\subsection{IEEE 14 Bus System}\label{subsec:NumSimIEEEBus}

@@

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We next consider a power network with $n=50$ generators, and propagate the transient joint state PDFs supported over the 100 dimensional state space $\mathbb{T}^{50}\times\mathbb{R}^{50}$. We take the initial joint state PDF at $t=0$ as
\begin{align}
\rho_{0}\equiv\rho(t=0,\theta(0),\omega(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\nonumber\\
	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\label{rho0synthetic}	
\end{align}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter ranges are consistent with the same found in \cite{sauerpai1998,andersonBook1977,kundurBook1994}.

@@

\bibitem{dorfler2012kron}
F.~Dorfler, and F.~Bullo, ``Kron reduction of graphs with applications to electrical networks", \emph{IEEE Transactions on Circuits and Systems I: Regular Papers}, Vol. 60, No. 1, pp. 150--163, 2012.

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.95\linewidth]{IEEE14marginals.png}
\caption{\small{Time evolution of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs, where $i=1,\hdots,5$, for the Kron-reduced IEEE 14 bus simulation setup described in Sec. \ref{subsec:NumSimIEEEBus}. The $5$ rows above correspond to the $5$ generator nodes; these are buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. The columns correspond to the time snapshots. The colorbar at the bottom shows the marginal PDF values.}}
\vspace*{-0.1in}
\label{fig:IEEE14marginals}
\end{figure*}

\begin{figure}[t]
\centering
\includegraphics[width=0.95\linewidth]{ComputationalTimeSyntheticIEEE14bus.png}
\caption{\small{The computational time for propagating the transient joint state PDFs over $\mathbb{T}^{5}\times\mathbb{R}^{5}$ for the simulation set up in Sec. \ref{subsec:NumSimIEEEBus}.}}
\vspace*{-0.1in}
\label{fig:CompTimeSynthetic}
\end{figure}

\subsection{IEEE 14 Bus System}\label{subsec:NumSimIEEEBus}
Following Sec. \ref{subsec:samplepathdynamics}, we consider the Kron-reduced dynamics \eqref{ItoSDEcomponentlevel} for the IEEE 14 bus system shown in Fig. \ref{fig:Motivating}. In this case, we have $n=5$ nodes which correspond to the buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. {\red{The parameter values in \eqref{DefParam} use the network reduced admittance matrix computed from the CITE?? The parameters $m_{i}, \gamma_{i}$ are obtained from ....}} We randomly generated $\sigma_{i}\in [1,5]$ as
\[(\sigma_{1},\hdots,\sigma_5) = \left(2.4628, 4.9266, 4.8724, 1.4215, 3.8681\right).\]

We take the initial joint PDF as
\begin{align}
\rho_{0}&\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = \vartheta_{0}\left(\bm{\theta}(0)\right)\Omega_{0}\left(\bm{\omega}(0)\right)\nonumber\\
&=\underbrace{\left(\prod_{i=1}^{n=5}\dfrac{\exp\left(\kappa_{i}\cos\left(2\theta_{i}(0)-\mu_{\theta_{i}(0)}\right)\right)}{2\pi I_{0}(\kappa_{i})}\right)}_{=:\vartheta_{0}\left(\bm{\theta}(0)\right)}\nonumber\\
	&\qquad\times \underbrace{{\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right)}_{=:\Omega_{0}\left(\bm{\omega}(0)\right)},
\label{rho0IEEE14}		
\end{align}
whose $\bm{\theta}$ marginal $ \vartheta_{0}\left(\bm{\theta}(0)\right)$ is a product von Mises PDF \cite{mardia2008multivariate,mardia2014some} supported over $\mathbb{T}^{5}$ with mean angles (in rad)
\begin{align}
\left(\mu_{\theta_{1}}(0),\hdots,\mu_{\theta_{5}}(0)\right)=\left(0, 6.1963, 6.0612, 6.0350, 6.0500\right),
\label{MeanAngleInitialIEEE14}	
\end{align}
and concentration parameter $\kappa_{i}\geq 0$ set as 
\[(\kappa_{1},\hdots,\kappa_5) = \left(5,6,7,4,5\right).\]
The mean angles \eqref{MeanAngleInitialIEEE14} were obtained as steady state power flow solutions {\red{for the generator phase angles with constant load?? Please complete/edit this sentence}} Larger $\kappa_{i}$ entails a larger concentration around the mean angle $\mu_{\theta_{i}}(0)$ (setting $\kappa_i=0$ implies that $\theta_{i}(0)$ follows uniform distribution over $[0,2\pi)$).

In \eqref{rho0IEEE14}, the $\bm{\omega}$ marginal $ \Omega_{0}\left(\bm{\omega}(0)\right)$ is a uniform PDF over $[-0.1,0.1]$ rad/s. Thus, the PDF $\rho_0$ in \eqref{rho0IEEE14} is supported over $\mathbb{T}^{5}\times [-0.1,0.1]$.

@@

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We next consider a power network with $n=50$ generators, and propagate the transient joint state PDFs supported over the 100 dimensional state space $\mathbb{T}^{50}\times\mathbb{R}^{50}$. We take the initial joint state PDF at $t=0$ as
\begin{align}
\rho_{0}\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\nonumber\\
	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\label{rho0synthetic}	
\end{align}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter ranges are consistent with the same found in \cite{sauerpai1998,andersonBook1977,kundurBook1994}.

@@

\bibitem{dorfler2012kron}
F.~Dorfler, and F.~Bullo, ``Kron Reduction of Graphs with Applications to Electrical Networks", \emph{IEEE Transactions on Circuits and Systems I: Regular Papers}, Vol. 60, No. 1, pp. 150--163, 2012.

% === von Mises PDF on n torus: Tn
\bibitem{mardia2008multivariate}
K.V.~Mardia, G.~Hughes, C.C.~Taylor, H.~Singh, ``A Multivariate von Mises Distribution with Applications to Bioinformatics", \emph{Canadian Journal of Statistics}, Vol. 36, No. 1, pp. 99--109, 2008.

\bibitem{mardia2014some}
K.V.~Mardia, and J. Voss, ``Some Fundamental Properties of a
Multivariate von Mises Distribution", \emph{Communications in Statistics - Theory and Methods}, Vol. 43, No. 6, pp. 1132--1144, 2014.
